rotation_runs2019

### 2019-10-09 inst/documents/rotations_notes.Rmd
improving experiment outputs
new simpler dispersal working

@@

migration limits ???
I need to check on them more ! to make sure I know what they are doing.
> RAF2 <- rot_migrate(RAF1gen, migration=1, coverage=0.1, verbose=TRUE)
  m.intervention f.intervention m.refugia f.refugia
1              1              1         0         0
2              1              1         0         0
3              1              1         0         0
  m.intervention f.intervention m.refugia f.refugia
1            0.1            0.1       0.1       0.1
2            0.1            0.1       0.1       0.1
3            0.1            0.1       0.1       0.1

>>>>

# 7/10/19
got diff insecticide runs working
Got mortality to appear properly in plots & key in non dispersal runs.

# 8/10/19 
added to readme

# 9/10/19

spent the day sweating over getting migration working.

Now I'm pleased I think it is simpler and I know what its doing.
Migration 1 is random mixing.

see the excel file for testing : rotations-dispersal-demo-andy201910.xlsx

@@

check on dispersal limits using new method. Seems that anything above 0.4 leads to near complete mixing
run_rot(migration=0.4, coverage=0.5)
#interesting how small levels of migration cause resistance freqs to decline even with no costs

write word description of what dispersal does
rename migration to dispersal ?

migration limits ???
I need to check on them more ! to make sure I know what they are doing.

RAF <- set_start_freqs(n=3, freqs=1)
> RAF1gen <- RAF[,,,1] # to view generation 1
> #set freqs in refugia to 0
> RAF1gen[,,'refugia']  <- 0
> #testing migration
> RAF2 <- rot_migrate(RAF1gen, migration=0.5, coverage=0.5, verbose=TRUE)
  m.intervention f.intervention m.refugia f.refugia
1              1              1         0         0
2              1              1         0         0
3              1              1         0         0
  m.intervention f.intervention m.refugia f.refugia
1           0.75           0.75      0.25      0.25
2           0.75           0.75      0.25      0.25
3           0.75           0.75      0.25      0.25

> RAF2 <- rot_migrate(RAF1gen, migration=1, coverage=0.1, verbose=TRUE)
  m.intervention f.intervention m.refugia f.refugia
1              1              1         0         0
2              1              1         0         0
3              1              1         0         0
  m.intervention f.intervention m.refugia f.refugia
1            0.1            0.1       0.1       0.1
2            0.1            0.1       0.1       0.1
3            0.1            0.1       0.1       0.1

~ consider renaming package to avoid conflict with CRAN rotations package insectrot rotinsect
